Statement-level AST-based Clone Detection in Java using Resolved Symbols

### 2019-11-06 benevol/paper.tex
Updates from Overleaf

Comparing code fragments including their contextual information introduces an optimization problem, as contextual information may be hard to retrieve. It can be ambiguous where contextual information resides and tracking it down may require to follow cross-file references. For large codebases, this can require a lot of time due to the sheer number of referenced symbols.

We propose a method to efficiently detect clones taking into account contextual information. To do this, we propose a tool that uses an AST-parsing library named JavaParser to detect clones a retrieve contextual information. Our method first parses the AST retrieved from JavaParser into a graph structure, which is then used to find clones. This graph maps the following relations for each statement in the codebase: the next statement, the previous statement, and the previous cloned statement.
\end{abstract}

@@

\section{Introduction}
%Most clone detection tools can be configured using thresholds. These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones. Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data~\cite{alves2010deriving}. Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
Duplicate code fragments are often considered as symptoms of bad design~\cite{fowler2018refactoring}. They create implicit dependencies, thus increasing maintenance efforts or causing bugs in evolving software. Changing one occurrence of such a duplicated fragment may require other occurrences to be changed as well~\cite{ostberg2014automatically}. Also, duplicated code has been shown to add up to 25\% of total system volume~\cite{bruntink2005use}, which entails more code to be maintained.

@@

\section{Background}
We use two concepts to argue about code clones~\cite{roy2007survey}:
\\ \textbf{Clone instance}: A single cloned fragment.
\\ \textbf{Clone class}: A set of similar clone instances.

@@

@@

\section{CloneRefactor}
We develop a tool named CloneRefactor\footnote{CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}} that detects clones that can (relatively) easily be refactored. This tool uses JavaParser~\cite{tomassetti2017javaparser} to build an AST and to find contextual information (e.g. resolve symbols). We then propose a novel clone detection technique to detect clones using JavaParser.

\section{JavaParser}
JavaParser~\cite{tomassetti2017javaparser} is a Java library which allows parsing Java source files to an abstract syntax tree (AST). JavaParser allows to modify this AST and write the result back to Java source code. The ultimate goal is to use this to be able to apply automated refactorings.

Integrated into JavaParser is a library named SymbolSolver. This library allows for the resolution of symbols using JavaParser. For instance, we can use it to trace references (methods, variables, types, etc) to their declarations (these referenced identifiers are also called ``symbols''). Using this, we can find the required contextual information.

\section{Clone Detection}\label{sec:clonedetection}
To detect clones, CloneRefactor parses the AST acquired from JavaParser to a graph structure. Based on this graph structure, clones are detected. Dependent on the type of clones being detected, transformations may be applied.

@@

\section{Results}
To compare the difference in detected clones when contextual information is considered, we

>>>>

Comparing code fragments including their contextual information introduces an optimization problem, as this information may be hard to retrieve. It can be ambiguous where contextual information resides and tracking it down may require to follow cross-file references. For large codebases, it could become time-consuming due to the sheer number of referenced symbols.

We propose a method to efficiently detect clones taking into account contextual information. We introduce a tool that uses an AST-parsing library named JavaParser to detect clones and retrieve contextual information. Our method parses the Abstract Syntax Tree retrieved from JavaParser into a graph structure, which is used to find clones. This graph maps the following relations for each statement in the codebase: the next statement, the previous statement, and the previous cloned statement.
\end{abstract}

@@

\section{Introduction}
%Most clone detection tools can be configured using thresholds. These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones. Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data~\cite{alves2010deriving}. Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
Duplicate code fragments are often considered as symptoms of bad design~\cite{fowler2018refactoring}. They create implicit dependencies, thus increasing maintenance efforts or causing bugs in evolving software. Changing one occurrence of a duplicated fragment may require other occurrences to be changed as well~\cite{ostberg2014automatically}. Also, duplicated code has been shown to add up to 25\% of total system volume~\cite{bruntink2005use}, which entails more code to be maintained.

@@

\section{Background}
\subsection{Code clones}
We use two concepts to argue about code clones~\cite{roy2007survey}:
\\ \textbf{Clone instance}: A single cloned fragment.
\\ \textbf{Clone class}: A set of similar clone instances.

@@

\section{JavaParser}
JavaParser~\cite{tomassetti2017javaparser} is a Java library which allows parsing Java source files to an abstract syntax tree (AST). Integrated into JavaParser is a library named SymbolSolver. This library allows for the resolution of symbols using JavaParser. For instance, we can use it to trace references (methods, variables, types, etc) to their declarations (these referenced identifiers are also called ``symbols''). Using this, we can find the required contextual information.

@@

\section{Clone Detection}\label{sec:clonedetection}
We develop a tool named CloneRefactor\footnote{CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}} that detects clones that can (relatively) easily be refactored. This tool uses JavaParser~\cite{tomassetti2017javaparser} to build an AST and to find contextual information (e.g. resolve symbols). We then propose a novel clone detection technique to detect clones using JavaParser.

To detect clones, CloneRefactor parses the AST acquired from JavaParser to a graph structure. Based on this graph structure, clones are detected. Dependent on the type of clones being detected, transformations may be applied.

@@

\section{Results}
To compare the difference in detected clones when contextual information is considered, we compared the number of clones found when considering contextual information with when it is not considered. For this, we use a corpus of 2.
